The symmetric \textit{Fermi} and eROSITA bubbles problem: A proof-of-concept study

### 2022-01-26 paper.tex
update

\begin{document}
\title{Title: A proof-of-concept study}

@@

\section{Introduction}
A decade after the discovery of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
the high resolution X-ray map \citep{Predehl2020} from eROSITA \citep{Predehl2021} also shows\
similar X-ray bubbles above and below the Galaxy,\
but about twice as large as the Fermi bubbles, each having a diameter of about 45,000 lightyears.\

@@

\subsubsection{Hadronic process}
In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be written as
\begin{equation}
   \epsilon \propto U_{\text{CRp}}n_{p}\sigma_{p}\kappa_{pp}.
\end{equation}

\begin{equation}
  \frac{dE}{dtd\epsilon_{1}dV} =\
   cn_{H}pC\left(\frac{\epsilon_{1}}{m_{\text{p}}c^2}\right)^{-p}\
   \int_{0}^{1}\sigma(\epsilon_{\text{p}}) F(x,\epsilon_{\text{p}}) x^{p}dx.
\end{equation}

\begin{equation}
\sigma(\epsilon_{\text{p}})=34.3+1.88L+0.25L^{2}\left[1-\frac{E_{\text{threshold}}}{E_{\text{p}}}\right]^{4} \text{ mb}.
\end{equation}

\begin{equation}
F(x,\epsilon_{\text{p}})=B\frac{d}{dx}\left[\ln(x)\left(\frac{1-x^{\beta}}{1+kx^{\beta}\left(1-x^{\beta}\right)}\right)^4\right],
\end{equation}

where
$x=\epsilon_{1}/\epsilon_{\text{p}}$, $B=1.30+0.14L+0.011L^2$, $\beta=\left(1.79+0.11L+0.008L^{2}\right)^{-1}$,\
$\left(0.801+0.049L+0.014L^{2}\right)^{-1}$, $L=\ln(\epsilon_{\text{p}}/1 \text{ TeV})$.

>>>>

\begin{document}
\title{The symmetric \textit{Fermi} and eROSITA bubbles problem: A proof-of-concept study}

@@

\section{Introduction}
Over the last decade the discovery of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
the high resolution X-ray map \citep{Predehl2020} from eROSITA \citep{Predehl2021} also shows\
similar X-ray bubbles above and below the Galaxy,\
but about twice as large as the Fermi bubbles, each having a diameter of about 45,000 lightyears.\

@@

%\subsubsection{Hadronic process}
%In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
%and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be written as
%\begin{equation}
%   \epsilon \propto U_{\text{CRp}}n_{p}\sigma_{p}\kappa_{pp}.
%\end{equation}
%
%\begin{equation}
%  \frac{dE}{dtd\epsilon_{1}dV} =\
%   cn_{H}pC\left(\frac{\epsilon_{1}}{m_{\text{p}}c^2}\right)^{-p}\
%   \int_{0}^{1}\sigma(\epsilon_{\text{p}}) F(x,\epsilon_{\text{p}}) x^{p}dx.
%\end{equation}
%
%\begin{equation}
%\sigma(\epsilon_{\text{p}})=34.3+1.88L+0.25L^{2}\left[1-\frac{E_{\text{threshold}}}{E_{\text{p}}}\right]^{4} \text{ mb}.
%\end{equation}
%
%\begin{equation}
%F(x,\epsilon_{\text{p}})=B\frac{d}{dx}\left[\ln(x)\left(\frac{1-x^{\beta}}{1+kx^{\beta}\left(1-x^{\beta}\right)}\right)^4\right],
%\end{equation}
%
%
%where
%$x=\epsilon_{1}/\epsilon_{\text{p}}$, $B=1.30+0.14L+0.011L^2$, $\beta=\left(1.79+0.11L+0.008L^{2}\right)^{-1}$,\
%$\left(0.801+0.049L+0.014L^{2}\right)^{-1}$, $L=\ln(\epsilon_{\text{p}}/1 \text{ TeV})$.
